Carbonate chemistry at Ny-Ålesund

### 2022-12-29 awipev-CO2.Rmd
K1K2 almost completed

@@

@@

The discrete values of AT, CT, salinity and temperature in the FerryBox
were used to calculate pH and pCO2 using the formulations for K1 and K2 of Lueker
et al. (2000) and Sulpis et al. (2020). The differences induced by the
choice of the carbonic acid constants are:

-   large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on
    average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`)
    compared with the uncertainty calculated with seacarb
    (`r round(errors[1, 7], digits = 3)`). In general, pH is higher with
    Sulpis than with Lueker.

-   small for pCO2 (`r round(diff_ls_quant[4, 3], digits = 1)` uatm on
    average; always lower with Sulpis than with Lueker) compared with
    the uncertainty calculated with seacarb
    (`r round(errors[2, 8], digits = 1)`)

@@

Here we compare pH measured spectrophotometrically with pH calculated
from AT and CT using various formulations of K1 and K2. All pH values
were normalized to a temperature of 4°C. The absolute differences are
generally large, up to
`r round(max(abs(diff_table_at_ct[, 2:5])), digits=3)` pH units. In
general, all formulations overestimate spectrophotometric pH. pH
calculated using the formulation of Papadimitriou et al. (2018) is
closer to measured pH, with a mean difference of
`r round(diff_table_at_ct[4, 4], digits=3)` pH units. This difference is
`r abs(round(diff_table_at_ct[4, 4]/errors_at_ct$pH, digits=1))` times
the uncertainty for pH calculated from AT and CT according to seacarb
(`r round(errors_at_ct$pH, digits=3)`). The differences found with the
other formulations are, on average, slightly lower than the uncertainty
for pH calculated from AT and CT according to seacarb.

>>>>

**_Comparison of various formulations compared to Lueker et al. (2000)_**

@@

**_Comparison of measured vs calculated pH_**

@@

**_Comparison of various formulations compared to Lueker et al. (2000)_**
The discrete values of AT, CT, salinity and temperature in the FerryBox
were used to calculate pH and pCO2 using various formulations for K1 and K2. The median 
differences induced by the choice of the carbonic acid constants are shiown below.

@@

**_Comparison of measured vs calculated pH_**
Here we compare pH measured spectrophotometrically with pH calculated
from AT and CT using various formulations of K1 and K2. All pH values
were normalized to a temperature of 4°C. The absolute differences are
generally large, up to
`r round(max(abs(diff_table_at_ct[, 2:5])), digits=3)` pH units. In
general, all formulations overestimate spectrophotometric pH. pH
calculated using the formulation of Papadimitriou et al. (2018) is
closer to measured pH, with a mean difference of
`r round(diff_table_at_ct[4, 4], digits=3)` pH units. This difference is
`r abs(round(diff_table_at_ct[4, 4]/errors_at_ct$pH, digits=1))` times
the uncertainty for pH calculated from AT and CT according to seacarb
(`r round(errors_at_ct$pH, digits=3)`). The differences found with the
other formulations are, on average, slightly lower than the uncertainty
for pH calculated from AT and CT according to seacarb.
